---
title: "Covariate selection_Ethiopia"
author: "Himal"
date: "19/06/2020"
output: 
  html_document:
    theme: united
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, echo=FALSE}
knitr::opts_knit$set(root.dir = "/Users/oshin/OneDrive - LA TROBE UNIVERSITY/Onchocerciasis")
```

The purpose of this code is to perform clustering analysis on covariates to check the multi-collinearity. Based on the clustering analysis, it returns the desired number of least collinear variables for load into the model.

These codes are based on a [published literature](https://www.nature.com/articles/s41586-019-1418-6).

```{r}
# Load the libraries without any messages
suppressMessages(library(ClustOfVar))
suppressMessages(library(tictoc)) # record all timings when a complex script is running
suppressMessages(library(tidyverse))
suppressMessages(library(caret)) # classification and regression training
```
Importing the data 

```{r}
data = read.csv("PhD/Data/eth_prev_data_c_covs.csv")
str(data)  # inspect the data
```

Isolate the covariate data without any of the dependent variables
```{r}
covariateDF = subset(data, select = -c(X, N, CASES, YEAR_START, LAT, LONG, DX_CODE, NID, DX_GROUP))
print("Covariate Variable Names")
print(colnames(covariateDF))
```

Examining the numbers of NAs
```{r}
numberofNAs = sapply(covariateDF, function(y)sum(length(which(is.na(y)))))
data.frame(numberofNAs)

# make the dataset with complete data
completeData = covariateDF[complete.cases(covariateDF),]
dim(completeData)
```

## Clustering
```{r}
tic()

# Run the clustering function and plot the variables
tree = hclustvar(X.quanti = completeData)
plot(tree)

toc()
```
Preparing desired number of clusters to generate. For now, I am preparing list of five, ten and fifteen covariates.
```{r}
numOfClusters = c(5,10,15) 
```

```{r}
emptyVarsList = list()  # empty list to store variables from clustering

for (nC in numOfClusters) {  # loop the clustering across the desired number of clusters
  set.seed(42) # set random seed number
  part = cutreevar(tree, nC) # top variables in each cluster
  midVariableList = c()  # Instantiate empty list to store variables
  # extract only the names of the variables
  namesListWithNulls = lapply(part$var, rownames)
  namesListWithoutNulls = Filter(Negate(function(x) is.null(unlist(x))),
                                 namesListWithNulls)
  # ascertain the top variables from the KMeans Clustering
  # and store it in a list
  for (j in c(1:length(namesListWithoutNulls))) {
    midVariableList[j] = namesListWithoutNulls[[j]][1]
  }
  
  # prep the variable list for input into the model calls
  varsToInclude = list((midVariableList))
  emptyVarsList[match(nC, numOfClusters)] = varsToInclude
}

print(emptyVarsList)
```

Not sure why it doesn't return the complete list of covariates we want. But, we can manually choose more covariates looking at the dendogram tree and also based on what's known from the literature.
